Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-04-01 WRITEUP/ms.tex
addressed AF's comments on Mcl > 1.e8 Msun

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/hist_test_16.pdf}
\caption{Number distribution of molecular gas density of \flower during the accreting phase shown in \Fig{SFH}{\em
    (b)}. 
\label{fig:h2density}}
\end{figure}

@@

To visually
%mm appreciate
    display 
the clump finding procedure, in \Fig{MCC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps.
Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MCC}) so that one can more easily see that they are collections of disjoint structures.
%
We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

Note that we impose the additional constraint that an identified
structure must be composed of at least 10 cells. We caution that an
important caveat of such a constraint is that we can only examine the
parameter space of cloud complexes of 
%mm typical size $R\gtrsim 60$\,pc [revised assuming spherical MCCs
%per Sect 4.2]
   radius $R\gtrsim 40$\,pc,
because of the resolution limit of the simulation.

\subsection{Molecular Cloud 
%mm
    Complex
Properties}

@@

We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest MCC.
%
We find $\sim$10--13 MCCs with masses exceeding 10$^8$\,\Msun across
all the evolutionary stages considered in this work, for each  $n_{\rm
  cut}$ value. \AF{This is true only for low $n_{cut}$? Why in Fig. do
  you show the valu 18.96 instead?} \DL{MCCs w/ Mcl $>$10$^8$\,\Msun
  is the case for each ncut.} \MM{I am afraid I am also confused by
  this, for two reasons.  First, if I understand the Figure, the
  highest $n_{\rm cut}$ shows no such large MCCs at any time.  Second,
  back in section 3, the H$_2$ mass of \flower was given as 5\E{7}
  \Msun, precluding the existence of even a single 10$^8$ \Msun
  cloud.} 
\DL{Since we don't resolve the molecular clouds, the clouds are not fully molecular. The $M_{\rm cl}$ here is more 
like total gas mass. AP will add disclaimer in Section 3. Will double check 
Mcl for all ncut and address AF's comment.}
  Such massive clouds correspond to the molecular disk of the
galaxy, which is identified as a single component for low $n_{\rm
  cut}$. The mass of the MCCs identified ranges between $M_{\rm
  cl}\simeq$10$^{5.5-8.5}$\,\Msun, consistent with those observed in
\z$\sim$2 galaxies in rest-frame UV and optical light
\citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and
  $f_{gas}$ here..Also, what is the total number of MCCs?} \MM{In the
  high-density plot, it looks like you have quite a number of
  unresolved clouds with $R < 40$~pc. Any idea what's going on there?}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Distributions of mass (left), size (middle), and gas mass
  fraction (right) of MCCs identified using the lowest $n_{\rm cut}$
  (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels)
%mm
      over all times analyzed here.
Note that the scalesshown on the $y$-axes are different between the top
and bottom panels, as fewer MCCs are identified at higher $n_{\rm
  cut}$. \MM{Put labels on the y-axis (maybe just $N$ or some such). Tick marks should point inwards
  rather than outwards.  I'd suggest putting the $n_{\rm cut}$ labels
  on the left panels following the style of the previous figure (and
  drop the brackets around the unit there). The $R$ axis could
  reasonably be pulled in to 250 pc, providing a bit more dynamic
  range at the low end.}
\label{fig:dist}}
\end{figure*}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/hist_test_16.pdf}
\caption{Distribution of molecular gas density of \flower during the accreting phase shown in \Fig{SFH}{\em
    (b)}. 
\label{fig:h2density}}
\end{figure}

@@

To visually display 
the clump finding procedure, in \Fig{MCC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps.
Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MCC}) so that one can more easily see that they are collections of disjoint structures.
%
We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

Note that we impose the additional constraint that an identified
structure must be composed of at least 10 cells. We caution that an
important caveat of such a constraint is that we can only examine the
parameter space of cloud complexes of 
radius $R\gtrsim 40$\,pc,
because of the resolution limit of the simulation.

\subsection{Molecular Cloud Complex Properties}

@@

The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to 
a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
However, not all evolutionary stages considered have at least one MCC at this highest density threshold, 
we therefore consider MCCs identified with the second highest density threshold  ($n_{\rm cut}$\eq18.96\,\cc) in the following. 
We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. 
%
\MM{The highest $n_{\rm cut}$ shows no such large MCCs ($>$10$^8$\,\Msun) at any time.  Second,
  back in section 3, the H$_2$ mass of \flower was given as 5\E{7}
  \Msun, precluding the existence of even a single 10$^8$ \Msun
  cloud.} 
\DL{Since we don't resolve the molecular clouds, the clouds are not fully molecular. The $M_{\rm cl}$ here is more 
like total gas mass. AP will add disclaimer in Section 3.}
  Such massive clouds correspond to the molecular disk of the
galaxy, which is identified as a single component for low $n_{\rm
  cut}$. The mass of the MCCs identified ranges between $M_{\rm
  cl}\simeq$10$^{5.5-8.5}$\,\Msun, consistent with those observed in
\z$\sim$2 galaxies in rest-frame UV and optical light
\citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and
  $f_{gas}$ here..Also, what is the total number of MCCs?} \MM{In the
  high-density plot, it looks like you have quite a number of
  unresolved clouds with $R < 40$~pc. Any idea what's going on there?}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Distributions of mass (left), size (middle), and gas mass
  fraction (right) of MCCs identified using the lowest $n_{\rm cut}$
  (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels)
%mm
      over all times analyzed here.
Note that the scalesshown on the $y$-axes are different between the top
and bottom panels, as fewer MCCs are identified at higher $n_{\rm
  cut}$. 
\label{fig:dist}}
\end{figure*}
